---
title: "Tuberculosis Incidence in 2016"
author: "Patrick Kelly"
date: "2/8/2019"
output: html_document
---
#Regions
### Eastern Africa (18 countries)
### Western Africa (16 countries)

### Data Sources

[Click Here](https://github.com/lukes/ISO-3166-Countries-with-Regional-Codes/blob/master/all/all.csv)"International Country Codes"

[Click Here](https://raw.githubusercontent.com/datamustekeers/WHOtb_data_analysis/master/data/TB_burden_countries_2018-07-04.csv)"WHO: Tuberculsis Incidence Data"

### Data from these two sources were merged to create the "tb_regions.csv" database for this analysis. This required harmonizing country names when they were different in the two data sources. 

```{r}
suppressMessages(library(data.table))
suppressMessages(library(dplyr))
suppressMessages(library(plotly))
suppressMessages(library(RCurl))
data <- getURL("https://raw.githubusercontent.com/damonzon/WHO_TB_Burden/master/tb_regions.csv")
regions <- read.csv(text = data)
East_Africa <- filter(regions, year == 2016 & region_code == "Eastern Africa" )
```

### Boxplot: Eastern Africa
```{r}
p <- ggplot(East_Africa, aes(x=1,y=incidence,
      country=Country,Incidence=incidence,
      pop=population)) + 
  geom_boxplot() +
  xlab("Eastern Africa: 18 Countries") +
  ylab("Tuberculosis Incidence in 2016") +
  theme_bw() +
  geom_jitter(shape=16, position=position_jitter(0.1),color="blue")+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggplotly(p,tooltip = c("country","Incidence","pop"))
```

### Barplot: Eastern Africa
```{r}
p <- ggplot(East_Africa, aes(x=reorder(Country,incidence), 
     y=incidence,country=Country,Incidence=incidence,
     pop=population)) +
     geom_bar(stat='identity', color="black", fill="blue") +
    coord_flip() +
    xlab("Eastern Africa: 18 Countries") +
    ylab("Tuberculosis Incidence in 2016") +
    theme_bw()
ggplotly(p,tooltip = c("country","Incidence","pop"))
```

##Western Africa
```{r}
Western <- filter(regions, year == 2016 & region_code == "Western Africa" )
```

### Boxplot: Western Africa
```{r}
p <- ggplot(Western, aes(x=1,y=incidence,
      country=Country,Incidence=incidence,
      pop=population)) + 
  geom_boxplot() +
  xlab("Western Africa: 16 Countries") +
  ylab("Tuberculosis Incidence in 2016") +
  theme_bw() +
  geom_jitter(shape=16, position=position_jitter(0.1),color="blue")+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
ggplotly(p,tooltip = c("country","Incidence","pop"))
```

### Barplot: Western Africa

```{r}
p <- ggplot(Western, aes(x=reorder(Country,incidence), 
     y=incidence,country=Country,Incidence=incidence,
     pop=population)) +
     geom_bar(stat='identity', color="black", fill="blue") +
    coord_flip() +
    xlab("Western Africa: 16 Countries") +
    ylab("Tuberculosis Incidence in 2016") +
    theme_bw()
ggplotly(p,tooltip = c("country","Incidence","pop"))
```

## Comment

### A Shiny application of this type of analysis would be very useful.
